Optimal amount of gut content data required to predict trophic interactions using a food web model

### 2022-03-01 manuscript/ms_C2/ms_C2.Rmd
minor

  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting interactions. And collecting and analysing these data from the field is an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data. 
  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.

>>>>

  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting the food web structure. And collecting and analysing these data from the field is an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data. 
  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.
